Preliminary Survey on Statistics and Software

### 2019-09-11 content/assignment/00-preliminary-survey.Rmd
Fix links to survey answers on survey page

- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/homeworks/00-preliminary-survey.pdf)
- [<i class="fas fa-external-link-square-alt"></i> `Answer Key`](/homeworks/00-preliminary-survey-answers-pdf.pdf)
- [<i class="fas fa-file-pdf"></i> `Answer Key`](/homeworks/00-preliminary-survey-answers.html)

>>>>

- [<i class="fas fa-file-pdf"></i> `Download as PDF`](/homeworks/00-preliminary-survey.pdf)
- [<i class="fas fa-external-link-square-alt"></i> `Answer Key (html)`](/homeworks/00-preliminary-survey-answers.html)
- [<i class="fas fa-file-pdf"></i> `Answer Key (PDF)`](/homeworks/00-preliminary-survey-answers-pdf.pdf)
